$K$-corrections and filter transformations \\ from the restframe ultraviolet to the near infrared

### 2005-08-24 docs/paper/kcorrect.tex
wrok on paper
git-svn-id: svn+ssh://howdy.physics.nyu.edu/usr/local/svn/kcorrect/trunk@493 75dff457-8751-0410-ab1a-cd701654ce6b

The templates do just as well on higher redshift data. For example,
Figure \ref{goods} shows the color residuals for GOODS data.

{\bf comparison to spectra}

>>>>

The templates do well on higher redshift data, as well. For example,
Figure \ref{goods} shows the color residuals for GOODS data. Here we
find that there are somewhat larger residuals with respect to the
uncertainties (again shown as the thick dashed lines). We can compare
this result to that in Figure \ref{goods_special}, which we get by
fitting to {\it only} the GOODS data (this alternate set of five
templates is also distributed in the manner that Appendix \ref{format}
describes). From Figure \ref{goods_special}, we conclude that {\it
some} of the errors are irreducible, and require either a larger set
of templates for high redshift galaxies (a possibility we find a
priori unlikely), or that there are simply errors in the catalogs or
the input filter curves. For example, in the $z$ and $V$ bands we find
significant trends between redshifts $z=0.5$ and $1.5$ (echoed in
Figure \ref{goods}. More significantly, in the $H$ band there is at
least a 10\% offset in the magnitudes across all redshifts, which is
almost certainly a catalog error.  {\bf GOODS people: this is your
challenge! what is going on?} Other errors (such as a large scatter in
the residuals in the $B$ band and some redshift dependence in the $J$
band) are clearly due to the fact that the templates are not primarily
designed for GOODS data. All in all, we recommend using the special
templates for $K$-corrections within the GOODS data set.

We can also test how well these templates recover actual spectra given
only photometry. To do so, we take eight random SDSS spectra (chosen
to span color space), project them onto the $g$, $r$ and $i$
bandpasses, and then fit the five templates to just these three
fluxes.  Figure \ref{specfit} compares the reconstructed model spectra
to the original spectrum. The two agree extremely well. Naturally,
this success depends heavily on the quality of the original stellar
spectra used in the population synthesis code of \citet{bruzual03a}.

### 2005-08-24 docs/paper/kcorrect_figures.tex
wrok on paper
git-svn-id: svn+ssh://howdy.physics.nyu.edu/usr/local/svn/kcorrect/trunk@493 75dff457-8751-0410-ab1a-cd701654ce6b

>>>>

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{goods.ps}
\caption{\label{goods} Color residuals in fit using the standard five
templates to GOODS data, compared to the typical uncertainties (thick
dashed lines). Note that the fits always do poorly on the $H$ band,
which we believe to be a catalog error. }
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{goods_special.ps}
\caption{\label{goods_special} Same as Figure \ref{goods}, but fitting
using five templates specially designed for GOODS. These templates
have smaller residuals in many respects but still fail to fit the $H$
band data. }
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{specfit.ps}
\caption{\label{specfit} Best fit model spectra based on the five
template fit to $g$, $r$ and $i$ fluxes, compared to the original
SDSS spectra from which we computed those fluxes.  The models and the
original spectra agree very well.}
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{twomass_resid.ps}
\caption{\label{twomass_resid} Similar to Figure \ref{fullfits} but
for galaxies observed in both SDSS and 2MASS and only using SDSS and
2MASS bands. }
\end{figure}

\clearpage
\stepcounter{thefigs}
\begin{figure}
\figurenum{\fignum}
\plotone{twomass_resid.ps}
\caption{\label{twomass_resid} Similar to Figure \ref{fullfits} but
for galaxies observed in both SDSS and 2MASS and only using SDSS and
2MASS bands. }
\end{figure}
